A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-13 paper/theor-experiment.tex
awa figure edits

\begin{figure}%[h]
	\centering
	\includegraphics[width=0.8\linewidth]{Report/timestep_comparison}
	\caption{Comparison of different fidelity models (dT stands for time step).}
	\label{tstep}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
	\caption{Pareto front comparing transverse beam size ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
	\label{fig:pareto1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
	}}
	\caption{Comparison of energy spread and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
	\label{fig:pareto2}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xyrms-zrms_newobj}\\
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
	\caption{Optimized beam sizes along high charge beam line.}
	\label{fig:stat}
\end{figure}

>>>>

\begin{figure}%[h]
	\centering
	\includegraphics[width=\linewidth]{Report/timestep_comparison}
	\caption{Comparison of different fidelity models (dT stands for time step).}
	\label{tstep}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
	\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
	\label{fig:pareto1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
	}}
	\caption{Pareto front comparing energy spread (dE) and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
	\label{fig:pareto2}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xyrms-zrms_newobj}\\
	\vspace{2em}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
	\caption{Optimized beam sizes along high charge beam line.}
	\label{fig:stat}
\end{figure}
